Dynein walks like an Imperial AT-ST

### 2018-08-05 papers/paper/paper.tex
Add new caption to paper.tex
Change paper_params eq angles and lengths to better match the burgess cryo-em figure; using model fitting in lieu of values reported from paper

\begin{figure*}[tbhp]
\includegraphics[width=0.3\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
\includegraphics[width=0.3\linewidth]{../../plots/chowdhury-model-figure.pdf}%
\includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}. \textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}. \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers.}
\label{fig:duration-length}
\end{figure*}

@@

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Ensure our experimental figures have at least one version with
  scale bars.
\item Write script to generate figures with cartoon on top of
  microscopy images.
\item Store our preferred geometric (and non-geometric) parameters in
  a python module, which is used both for creating figures (see above)
  and for running simulations.
\item Python script to write out latex with parameters.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\end{enumerate}

>>>>

\begin{figure*}[tbhp]
\includegraphics[width=0.3\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
\includegraphics[width=0.3\linewidth]{../../plots/chowdhury-model-figure.pdf}%
\includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}. \textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}. \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers. Left figure has a scale bar of 15nm, middle 25nm and right 28.8nm between the two binding domains.}
\label{fig:duration-length}
\end{figure*}

@@

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\item Figure out which of the model-em subfigures to include/remove
\end{enumerate}
